---
name: Jason G.
surname: Wallace
position: "Associate Professor"
address: "Department of Crop & Soil Sciences, University of Georgia"
phone: +1-706-542-9696 
www: wallacelab.uga.edu
email: "jason.wallace@uga.edu"
#twitter: TheWallaceLab
github: jgwall
linkedin: "jason-wallace-a874b845"
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::hyndman       # Not bad, but a little ugly with title bar
csl: 
header-includes:
  \definecolor{headcolor}{HTML}{000099}
  \usepackage{tabularx}
  \usepackage{float}
  \usepackage{colortbl}
  \usepackage{makecell}
  \hypersetup{colorlinks=true, urlcolor=headcolor}
  \urlstyle{same}
  \usepackage{xltabular}
  #\usepackage{titlesec} # Causes problems with "option clash" error
# Add more packages with tinytex::tlmgr_install('PACKAGE_NAME')

# TODO: Can also use Bookdown to separate out sections. Not necessary as currently written, but would help if want to include plaint-text stuff somewhere.
# TODO: Where put Carpentries' Classes? -> Guest lectures? Service to University? Workshops as separate thing?

---

<!-- Formatting LaTeX commands -->
\renewcommand{\labelitemi}{\textbullet}  <!-- Reset bullets to round circles -->

\setlist{nosep,after=\vspace{-\baselineskip}}  <!-- Don't skip a line after lists finish -->
\setlength{\LTpre}{0pt}  <!-- Remove extra space before longtable -->
\setlength{\LTpost}{0pt} <!-- Remove extra space after longtable  -->
<!-- Below supposed to change \paragraph formatting (=level 4 header) but doesn't -->
<!-- \renewcommand\paragraph{\@startsection{paragraph}{4}{\z@}% -->
<!--             {-2.5ex\@plus -1ex \@minus -.25ex}% -->
<!--             {1.25ex \@plus .25ex}% -->
<!--             {\normalfont\normalsize\bfseries\itshape}} -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, results="asis") # results='asis' lets latex code be interpreted properly
library(vitae)
library(dplyr)
library(readr)
library(rcrossref)
library(tibble)
library(kableExtra)
library(bibtex)
library(tidyr)
library(scales)

# Function to make sure any special characters are dealt with first
sanitize = function(tbl, ignore=NULL){
  to_change = names(tbl)
  to_change = to_change[!to_change %in% ignore]
  tbl %>% mutate_at(.vars=to_change, dplR::latexify, doublebackslash = FALSE)
}

# Helper function to load a CSV and do routine tasks
load_data = function(infile, ...){
  read_csv(infile, show_col_types=FALSE) %>% sanitize(...)
}

# Helper function to format text
bold = function(x){
  paste("\\textbf{", x, "}", sep="")
}
italic = function(x){
  paste("\\emph{", x, "}", sep="")
}
link = function(link, text){
  paste("\\href{", link, "}{", text, "}", sep="")
}

# Function to produce very basic table, no lines or headings - From Rob Hyndman, https://github.com/robjhyndman/CV, with modifications
baretable <- function(tbl, digits = 0,
                      include.colnames = FALSE, include.rownames = FALSE,
                      hline.after = NULL, size = getOption("xtable.size", NULL),
                      add.to.row = getOption("xtable.add.to.row", NULL), 
                      #tabular.environment="tabularx",
                      tabular.environment="xltabular", # Can experiment with this later
                      width = "\\textwidth",
                      ...) {
  xtable::xtable(tbl, digits = digits, ...) %>%
    print(
      include.colnames = include.colnames, include.rownames = include.rownames,
      hline.after = hline.after,  comment = FALSE,
      tabular.environment = tabular.environment,
      floating = FALSE, size = size, add.to.row = add.to.row,
      width=width,
      sanitize.text.function = function(x) {x}
    )
}


```

# Academic History
```{r header_info}
load_data("sources/0_header_info.csv") %>%
  mutate(info = bold(info)) %>%
  baretable()
```

## Education
```{r education}
load_data("sources/education.csv") %>%
  mutate(degree = bold(paste(degree, "\\textendash{}", location)), .keep="unused") %>%
  relocate(year, degree) %>%
  arrange(desc(year)) %>% # Arrange in descending order of Year
  baretable()
```

## Professional Experience
```{r employment}
load_data("sources/employment.csv") %>%
  arrange(desc(stop)) %>%
  mutate(time=paste(start, "\\textendash{}", stop, sep=""),
         title=bold(title),
         location=paste(organization, " (", location, ")", sep=""), .keep="unused") %>%
  relocate(time, title) %>%
  baretable()
```


## Awards
```{r awards}
load_data("sources/awards.csv") %>%
  relocate(when) %>%
  mutate(award=bold(award)) %>%
  baretable(align=c("llXl"))
```

# Instruction

## Instructor of Record
```{r teaching_mine}
schedule_to_bullets=function(class, schedule){
  bullets = paste(" \\item", schedule, sep=" ", collapse=" ")
  bullets = paste("\\begin{itemize}", bullets, "\\end{itemize}")
  paste(unique(class), bullets)
}

# Load and format
load_data("sources/teaching_mine.csv")  %>%
  mutate(class = bold(class),
         credits=paste(credits, ifelse(credits==1, "credit", "credits"))) %>%
  group_by(code) %>%
  summarize(class = schedule_to_bullets(class, schedule), credits=unique(credits)) %>%
  baretable(align=c("llXl")) # Have to specify column width for bullets to work ("X" = variable, but still works)
```

## Guest Lectures
```{r teaching_guest}
load_data("sources/teaching_guest.csv") %>%
  mutate(description = paste(bold(title), " (", class, ")", sep=""), .keep="unused") %>%
  relocate(date) %>%
  baretable()
```

## Student Mentorship
```{r student_mentorship}
# Note: throws error if not saved to variable
students=load_data("sources/students_grads.csv") %>%
  arrange(desc(year)) %>%  # Sort newest to oldest
  mutate(role = paste(role, " (", status, ")", sep=""),
         name=bold(name),
         department = ifelse(is.na(notes), department, paste(department, " (", notes, ")", sep="")), #Add notes in if present
         .keep="unused") %>%
  relocate(degree, year) %>%
  group_by(role) %>%
  group_map(function(x, ...){
    cat("###", unique(x$role), "\n")
    x %>% select(-role) %>%
      #baretable(align="llllX")
      baretable(align=c("l", "p{1.5em}", "p{5em}", "p{11em}", "X"))
  }, .keep=TRUE)
```

### Visiting Scientists
```{r visitors}
visitors = load_data("sources/visiting_scientists.csv") %>%
  mutate(name=bold(name)) %>%
  relocate(date) %>%
  baretable()
```

### Undergraduate Mentoring
```{r undergrads}
load_data("sources/students_undergrads.csv") %>%
  #mutate(name=bold(name)) %>%
  mutate(name=bold(name), role=paste(role, " (", university, ")", sep=""), .keep="unused") %>%
  relocate(date) %>%
  baretable()
```

### High School Students
```{r highschool}
load_data("sources/students_highschool.csv") %>%
  mutate(name=bold(name)) %>%
  select(-grade_level) %>%
  relocate(date, name) %>%
  baretable()
```

# Scholarly Activities

## Publications
```{r download_pubs, cache=TRUE, cache.extra = tools::md5sum('sources/pubs.articles.csv')}
# Load publications from CrossRef. Cache options mean only runs if source file or this chunk's code have changed
pubs = read.csv("sources/pubs.articles.csv")
citations = unlist(cr_cn(pubs$doi, format="bibtex")) %>%
  gsub(pattern="$\\less$i$\\greater$", repl="\\emph{", fixed=TRUE) %>% # Fix fonio genome title
  gsub(pattern="$\\less$/i$\\greater$", repl="}", fixed=TRUE)
write(citations, "sources/pubs.articles.bib")
```


```{r load_pubs}
# Load publications into R
pubdata = read.csv("sources/pubs.articles.csv", row.names="doi", check.names=FALSE)
rownames(pubdata) = tolower(rownames(pubdata))
pubs = bibliography_entries("sources/pubs.articles.bib")
pubs = pubs %>% arrange(desc(issued)) %>%
  mutate(year=format(as.Date(issued), format="%Y"),
         DOI=tolower(DOI),
         period = pubdata[DOI, "period"],
         type = pubdata[DOI, "article_type"])
#pubs$URL = paste("\\href{", pubs$URL, "}{", pubs$URL, "}", sep="")
```

```{r summarize_pubs}
# Summary table of publications

# Table output; "hold_position" argument keeps it in place, not top of page
pub.summary = table(pubs$period, pubs$type) %>%
  as.data.frame.matrix() %>%
  relocate(research, review, book_chapter) %>%
  rename("Research Article"=research, Review=review, "Book Chapter"=book_chapter)
pub.summary = pub.summary[rev(unique(pubdata$period)),]
pub.totals = pub.summary %>%
  summarize_all(sum)
rownames(pub.totals) = "Total"

pub.summary %>%
  rbind(pub.totals) %>%
  kbl(booktabs=TRUE) %>%
  kableExtra::kable_styling(latex_options = c("hold_position")) %>%
  row_spec(nrow(pub.summary), hline_after=TRUE) %>% # Separate from "totals"
  row_spec(nrow(pub.summary)+1, italic=TRUE, background="white", align="r") # Change format for "totals" row

```


```{r print_pubs}
# NOTE: only actually prints entries if printed in full elsewhere. Made workaround in next chunk.
for(myperiod in unique(pubs$period)){
  count = sum(pubs$period==myperiod)
  cat("### ", myperiod, " (", count, ")\n", sep="")
  pubs %>% filter(period==myperiod) %>%
    vitae:::knit_print.vitae_bibliography() %>%
    cat()
}
# TODO: Figure out how to indicate if I'm senior/corresponding author, bold my name, and underline lab members. (Latter two may have to be a lua filter apparnetly)
# TODO: More control if I do this myself (to add bold, asterisks, etc?). Harder to change bibliography method, so keep commented out if need that for some reason.
```

```{r print_pubs_dummy, include=FALSE}
# Workaround to needing a full printing for things to be included.
# This doesn't show up, but it apparently gets everything placed properly to show
pubs
```

## Meetings attended
_\* = speaker, † = poster, § = international scope_

```{r meetings}
meetings = load_data("sources/meetings.csv", ignore="date") %>%
  mutate(date=as.Date(date), year = format(date, "%Y")) %>%
  mutate(international=ifelse(is.na(international), FALSE, international))# Take care of using missing for F
blank="\\textcolor{white}{\\_}"

for(myperiod in rev(unique(meetings$period))){
   cat("###", paste(myperiod, " (", sum(meetings$period==myperiod), ")", sep=""),"\n")
   submeetings = meetings %>% filter(period==myperiod)
   
   for(myyear in sort(unique(submeetings$year), decreasing = TRUE)){
     cat("####", paste(myyear, " (", sum(submeetings$year==myyear), ")", sep=""),"\n")
     submeetings %>% 
        filter(year==myyear) %>%
        select(-period, -year) %>%
        arrange(desc(date)) %>%
        mutate(speaker=ifelse(grepl("speaker", present), "*", blank),
               poster=ifelse(grepl("poster", present), "†", blank),
               international=ifelse(international=="TRUE", "§", blank),
               description=paste(bold(meeting), "; ", location, " (", format(date, "%B %Y"), ")", sep=""), .keep="none") %>%
        mutate(codes=paste(speaker, poster, international, sep=""), .keep="unused") %>%
        relocate(codes, description) %>%
        baretable(align=c("l", "l", "X"))
   }
}

```

## Invited Presentations 
_§ = international scope_

```{r presentations}
presents = load_data("sources/presentations.csv", ignore="date") %>%
  mutate(international = ifelse(is.na(international), FALSE, international)) %>% # Remove NAs
  mutate(date=as.Date(date), international=ifelse(international, yes="§", no="")) %>%
  arrange(desc(date)) %>%
  mutate(date = format(date, "%d %b %Y"),
         #title = paste(international, bold(title), ". ", event, " (", location, ").", sep=""),
         title = paste(bold(title), ". ", event, " (", location, ").", sep=""),
         .keep="unused") %>%
  relocate(date, international, title)

for(myperiod in unique(presents$period)){
  count = sum(presents$period==myperiod)
  cat("### ", myperiod, " (", count, ")\n", sep="")
  presents %>% filter(period==myperiod) %>%
    select(-period) %>%
    baretable(align=c("l", "l", "l", "X"))
}
```


## Posters & Abstracts

```{r posters}
posters = load_data("sources/posters_and_abstracts.csv", ignore="date") %>%
  mutate(international = ifelse(is.na(international), FALSE, international)) %>% # Remove NAs
  mutate(date=as.Date(date), international=ifelse(international, yes="*", no="")) %>%
  arrange(desc(date)) %>%
  mutate(date = format(date, "%d %b %Y"),
         title = paste(international, authors, " ", bold(title), ". ", event, " (", location, ").", sep=""),
         .keep="unused")

for(myperiod in unique(posters$period)){
  count = sum(posters$period==myperiod)
  cat("### ", myperiod, " (", count, ")\n", sep="")
  posters %>% filter(period==myperiod) %>%
    select(-period) %>%
    baretable(align=c("l", "l", "X"))
}
```

## Other Creative Contributions
```{r creative_contributions}
creatives = load_data("sources/pubs.creative_contributions.csv", ignore="date") %>%
  mutate(date=as.Date(date)) %>%
  arrange(desc(date)) %>%
  mutate(date = format(date, "%d %b %Y"),
         description = paste(authors, bold(link(url, title))), .keep="unused") %>%
  relocate(date, description, type) %>%
  baretable(align=c("l", "l", "X", "l"))
```


# Research Grants
```{r grants_summary}
#TODO: go through and double-check amounts. See conflicts between my grant-tracking and my tenure package
# TODO: Fix fescue PGRP amounts after Noble withdraw

# Calculate grant totals
grants=load_data("sources/grants.csv", ignore=c("start", "stop", "submitted")) %>%
  mutate_at(c("amount_all", "amount_wallace"), as.numeric) %>%
  mutate_at(c("start", "stop", "submitted"), as.Date) %>%
  arrange(desc(submitted))
totals = grants %>%
  filter(status=="Current" | status=="Finished") %>%
  group_by(period, role) %>%
  summarize(total_all=sum(amount_all, na.rm=TRUE), total_wallace=sum(amount_wallace, na.rm=TRUE)) %>%
  pivot_wider(names_from=role, values_from=c(total_all, total_wallace)) %>% 
  rename(all_copi=`total_all_Co\\mbox{-}PI`, all_pi=total_all_PI,
           mine_copi=`total_wallace_Co\\mbox{-}PI`, mine_pi=total_wallace_PI) %>%
  relocate(period, all_pi, mine_pi, all_copi, mine_copi) %>%
  mutate(total_all = all_pi + all_copi, total_mine = mine_pi + mine_copi)

# Totals for below
totals.sum = select(totals, -period) %>%
  mutate(period="Totals") %>%
  summarize_all(sum, na.rm=TRUE)

# Format pretty
accent_color="headcolor"
totals %>%
  rbind(totals.sum) %>%
  mutate_if(is.numeric, dollar)  %>%
  kbl(booktabs=TRUE, col.names=NULL) %>%
  kableExtra::kable_styling(latex_options = c("hold_position")) %>%
  add_header_above(c(" ", "Total", "Wallace Lab", "Total", "Wallace Lab", "Total", "Wallace Lab"), 
                   color=c(rep("black",5), rep(accent_color,2)),
                   bold=c(rep(FALSE,5), rep(TRUE,2)), 
                   italic=c(rep(FALSE,5), rep(TRUE,2))) %>%
  add_header_above(c(" ", "PI"=2, "Co-PI"=2, "Totals"=2), bold=TRUE,
                   italic=c(F,F,F,T),
                   color=c("black","black", "black", accent_color)) %>%
  column_spec(1, bold = T) %>%
  row_spec(nrow(totals), hline_after=TRUE) %>% 
  row_spec(nrow(totals)+1, italic=TRUE, color=accent_color) %>% # Change format for "totals" row
  column_spec(6:7, italic=TRUE, bold=TRUE, color=accent_color) 
  
# Grand totals
grand = paste(bold("Total grants: "), 
              dollar(totals.sum$all_pi + totals.sum$all_copi, prefix="\\$"), "; ", 
              bold("Total to Wallace: "), 
              dollar(totals.sum$mine_pi + totals.sum$mine_copi, prefix="\\$"), sep="") 
#cat("\\begin{center}",grand,"\\end{center}\n")
```

## Pending
```{r grants_pending}
month_year=function(x){
  as.Date(x) %>% format("%b %Y")
}

# Helper function to format grants. include_mine does whether or not to include my portion
format_grants=function(x, include_mine=TRUE){
  x = x %>% mutate(mine_desc = ifelse(is.na(amount_wallace) | !include_mine, 
                                      yes=paste(" (", source, ")", sep=""),
                                      no=paste(" (", source, "; ",
                                               dollar(amount_wallace, prefix="\\$"), 
                                               " to Wallace)", sep="")), .keep="all" )
  x %>%
    mutate(role=role,
           amount=dollar(amount_all, prefix="\\$"),
           description = paste(bold(title), mine_desc,". ", 
                               month_year(start), "-",
                               month_year(stop), ".",
              sep=""), .keep="none") %>%
    baretable(align=c("l", "l", "r", "X"))
}

pending = grants %>% filter(status=="Pending")
if(nrow(pending)==0){
  cat("[None currently]\n")
}else{
  format_grants(pending)
}
```

## Funded
```{r grants_funded}
funded = grants %>% filter(status=="Current" | status=="Finished")
for(myperiod in unique(funded$period)){
   cat("###", myperiod,"\n") 
   funded %>% filter(period==myperiod) %>% 
     select(-period) %>% 
     format_grants()
}
  
```

## Submitted but unfunded
```{r grants_unfunded}
unfunded = grants %>% filter(status=="Declined")
for(myperiod in unique(unfunded$period)){
   cat("###", myperiod,"\n") 
   unfunded %>% filter(period==myperiod) %>% 
     select(-period) %>% 
     format_grants()
}
```





# Professional Development
```{r prof_development}
load_data("sources/professional_development.csv", ignore="date") %>%
  mutate(date=format(as.Date(date), "%d %b %Y"), description = paste(bold(title), ". \\newline ", description, ". (", location, ")", sep=""), .keep="none") %>%
  #select(-organization) %>%
  relocate(date, description) %>%
  baretable(align=c("l", "l", "X"))
```

# Academic Service

## Service to the University

### University Organizational Membership
```{r membership_university}
load_data("sources/membership_university.csv") %>%
  arrange(!is.na(stop), desc(stop), desc(start), organization) %>%
  mutate(
    stop=ifelse(is.na(stop), "Present", stop),
    sep="--",
    organization = bold(organization), 
    .keep="unused") %>%
  relocate(start, sep, stop, organization) %>%
  baretable(align=c("l", "l", "c", "l", "X"))
```

### University Leadership & Administration
```{r service_university}
load_data("sources/service_university.csv", ignore=c("start", "stop")) %>%
  #arrange(!is.na(stop), desc(as.Date(start))) %>%
  arrange(!is.na(stop), desc(stop), desc(as.Date(start))) %>%
  mutate(
    start=format(as.Date(start), "%b %Y"),
    stop=ifelse(is.na(stop), "Present", format(as.Date(stop), "%b %Y")),
    sep="--",
    description = paste(bold(description), ", ", unit, sep=""), 
    .keep="unused") %>%
  relocate(start, sep, stop, description) %>%
  baretable(align=c("l", "l", "c", "l", "X"))
  
# Deprecated reformat where have start-stop as one column instead of separate ones
  # mutate(
  #   date=paste(format(as.Date(start), "%b %Y"), ifelse(is.na(stop), "Present", format(as.Date(stop), "%b %Y")), sep="--"), 
  #                   description = paste(bold(description), ", ", unit, sep=""), .keep="unused") %>%
  # relocate(date, description) %>%
  # baretable(align=c("l", "l", "X"))
```

## Service to the Scientific Community

### Editorships
```{r editorships}
load_data("sources/editorships.csv", ignore=c("start", "stop")) %>%
  arrange(!is.na(stop), desc(stop), desc(as.Date(start))) %>%
  mutate(
    start=format(as.Date(start), "%b %Y"),
    stop=ifelse(is.na(stop), "Present", format(as.Date(stop), "%b %Y")),
    sep="--",
    description = paste(bold(role), ", ", italic(organization), sep=""), 
    .keep="unused") %>%
  relocate(start, sep, stop, description) %>%
  baretable(align=c("l", "l", "c", "l", "X"))
```

### Invited External Review
```{r invited_reviews}
# Header by period, then make a table with "type (total)" and "[list of orgs with (total) each if >1]"
reviews = load_data("sources/service_reviewing.csv")
for(myperiod in unique(reviews$period)){
   cat("####", myperiod,"\n") 
   reviews %>% filter(period==myperiod) %>% 
     select(-period, -year, -notes) %>% 
     count(type, organization) %>%
     mutate(organization = paste(organization, ifelse(n>1, paste(" (",n,")", sep=""), ""), sep="")) %>%
     group_by(type) %>%
     summarize(type = paste(type, " (", sum(n), ")", sep=""), 
               organization = paste(sort(organization), sep="", collapse=", ")) %>%
     unique() %>%
     baretable(align=c("l","l","X"))
}

```

### Society memberships
```{r societies}
societies = load_data("sources/membership_societies.csv") %>%
  arrange(organization, start) %>%
  mutate(stop=ifelse(is.na(stop), "Present", stop)) %>%
  mutate(dates=paste(start, stop, sep="-"), organization=bold(organization), .keep="none") %>%
  relocate(dates, organization) %>%
  group_by(organization) %>%
  summarize(dates = paste(dates, collapse="; ")) %>%
  mutate(organization = paste(organization, " (", dates, ")", sep=""), .keep="none") %>%
  baretable(align=c("l","X"))
```

## Public Outreach and Service
```{r outreach}
outreach = load_data("sources/outreach.csv", ignore="date") %>%
  arrange(desc(date)) %>%
  mutate(num_participants = ifelse(is.na(num_participants), yes="", 
                                   no=paste(num_participants, "participants; ")),
         link = ifelse(is.na(link), yes="",
                       no=paste(" (",link(link, "link"), ")", sep=""))) %>%
  mutate(date=format(date, "%d %b %Y"), 
         description=paste(bold(event), " (", num_participants, location, ")",
                           link,"  \\newline ", description, sep=""), .keep="none") %>%
  baretable(align=c("l","l", "X"))
```

<!-- # TODO: Major Accomplishments -->

<!-- \badcommand -->